A thesis draft

### 2018-11-24 res/sections/07-Introduction.tex
Fix typos

This thesis is organized as follows:
\begin{itemize}
 \item Chapter~\ref{chap:background} describes background information about 5G
   and the technologies used to build an ETSI compliant architecture;
 \item Chapter~\ref{chap:rel_wk} gives an insight of correlated works on this
   field;
 \item Chapter~\ref{chap:prjan} explains the analysis performed on the
   requirements provided and the design choices performed;
 \item Chapter~\ref{chap:archimpl} provides an in-depth view of the high-level
   architectural implementation;
 \item Chapter~\ref{chap:vnf_ns_impl} gives a bief explanation of the VNF and NS
   implementation;
 \item Chapter~\ref{chap:test} describes the tests done on the plaftorm;
 \item Chapter~\ref{chap:conclusions} wraps up the overall project experience.
\end{itemize}

>>>>

This thesis is organized as follows:
\begin{itemize}
 \item Chapter~\ref{chap:background} describes background information about 5G
   and the technologies used to build an ETSI compliant architecture;
 \item Chapter~\ref{chap:rel_wk} gives an insight of correlated works on this
   field;
 \item Chapter~\ref{chap:prjan} explains the analysis performed on the
   requirements provided and the design choices performed;
 \item Chapter~\ref{chap:archimpl} provides an in-depth view of the high-level
   architectural implementation;
 \item Chapter~\ref{chap:vnf_ns_impl} gives a brief explanation of the VNF and NS
   implementation;
 \item Chapter~\ref{chap:test} describes the tests done on the platform;
 \item Chapter~\ref{chap:conclusions} wraps up the overall project experience.
\end{itemize}
